Working document to try to explain why/how ATAs influence coexistence in an intuitive way for referee 3

### 2023-07-28 paper/ExplanationOfATAEffectsWorkingDoc.tex
just added a figure for the lognormal fecundities model

We now use Fig. \ref{fig:beta_fecundidities_explanatory} to explain ATAs. Coexistence is possible for 
right-tail association (panel F, positive GWR) but impossible for left-tail association (D,
negative GWR). Coexistence is possible for the right-tail case essentially
because the points on the ``left'' region in C produce highly variable
annual growth rates; the same effect does not occur for the left-tail case because 
points in the ``left'' region on panel A are concentrated on line $L_1$ because of the
strong left-tail association of $E_i$ and $C_{i \bs i}$ on that panel. 
Association, or lack thereof, in right tails makes essentially no difference 
to growth rates because $E_i/C_{i \bs i}$ cannot vary much. Overall, ATA effects 
are positive for the right-tail case because strong association between 
$E_i$ and $C_{i \bs i}$ is concentrated in the right tails, where there 
is little potential for storage effects; and so disassociation between
$E_i$ and $C_{i \bs i}$ in the left tails, where there is much potential for
storage effects, can be stronger. For the actual quantification of ATA effects,
a comparison is made to the case of symmetric association 
(panels B, E), as a benchmark. What is assessed by our quantification of ATA
effects is essentially the degree to which patterns of disassociations between 
$E$ and $C$, which can cause storage effects, align with the portions of 
the $E,C$ distribution for which the potential for storage effects is highest,
with larger ATA effects indicating better alignment, such as in panels C, F
of Fig. \ref{fig:beta_fecundidities_explanatory}.

@@

>>>>

We now relate Fig. \ref{fig:beta_fecundidities_explanatory} back to ATAs. Coexistence is possible for 
right-tail association (panel F, positive GWR) but impossible for left-tail association (panel D,
negative GWR). Coexistence is possible for the right-tail case essentially
because the points in the ``left'' region in C produce highly variable
annual growth rates, which lead to storage effects; the same effect does 
not occur for the left-tail case because 
points in the ``left'' region on panel A are concentrated on line $L_1$ because of the
strong left-tail association of $E_i$ and $C_{i \bs i}$ on that panel. 
Association, or lack thereof, in right tails makes little difference 
to mean growth rates because $E_i/C_{i \bs i}$ cannot vary much. Overall, ATA effects 
are positive for the right-tail case because strong association between 
$E_i$ and $C_{i \bs i}$ is concentrated in the right tails, where there 
is little potential for storage effects anyway; and so disassociation between
$E_i$ and $C_{i \bs i}$ occurs in the left tails, where there is much potential for
storage effects. For the actual quantification of ATA effects,
a comparison is made to the case of symmetric association 
(panels B, E), as a benchmark. What is assessed by ATA
effects is the degree to which patterns of disassociation between 
$E$ and $C$ align with the portions of $E,C$ distribution for which the potential
for storage effects is high. Larger ATA effects indicate better alignment.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/PostHocExplanatoryFig_lognormalFecund.jpg}
\caption{A detailed look at ATA effects for the log-normal fecundities lottery model.
Similar to Fig. \ref{fig:beta_fecundidities_explanatory}, but for the 
log-normal fecundities lottery model instead of the beta fecundities
lottery model. See SI section X2
%***DAN: fix this link when you put the text into the paper
for details. We used model parameters $\sigma = 1$, $\mu_1 = 0$, $\mu_2=0.5$, 
and $\delta=0.6$ for this example.}\label{fig:lognormal_fecundidities_explanatory}
\end{figure}
